Impact of the 2016 Presidential Election on Urban Mobility: Who is Affected the Most?

### 2019-11-11 proposal.Rmd
dataset prepared

```{r setup, include=FALSE}
# library(tidyverse)
# library(sf)
# 
# travel_times <- read_csv(file = "data/boston-censustracts-2019-3-All-HourlyAggregate.csv")
# shapes <- st_read(dsn = "data/boston_censustracts.json")
```

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(sf)

travel_times <- read_csv(file = "data/washington_DC_travel_times.csv")
```
